My JuliaCon proceeding

### 2023-05-31 paper.tex
Minor notes on RxInfer

%% --- autogenerated TOC ---
% juliacon
% document
%   Introduction
%   To Kill a Floating Point
%     Where do NaNs come from?
%     NaN kills
%   FloatTracker Internals
%     Catching NaN kills
%     NaN propagation monitoring
%     NaN injection
%   Case Studies
%     Surprise NaNs: ShallowWaters
%     NaN fuzzing to find a kill: OrdinaryDiffEq
%     NaN Kills: Finch
%   Evaluation
%   Discussion
%   Related Work
%   Acknowledgments
% document
%% --- end autogenerated TOC ---

@@

@@

>>>>

%% --- autogenerated TOC ---
% juliacon
% document
%   Introduction
%   To Kill a Floating Point
%     Where do NaNs come from?
%     NaN kills
%   FloatTracker Internals
%     Catching NaN kills
%     NaN propagation monitoring
%     NaN injection
%   Case Studies
%     Surprise NaNs: ShallowWaters
%     NaN fuzzing to find a kill: OrdinaryDiffEq
%     NaN Kills: Finch
%     A Bug-Hunting Safari
%   Evaluation
%   Discussion
%   Related Work
%   Acknowledgments
% document
%% --- end autogenerated TOC ---

@@

\subsection{A Bug-Hunting Safari}

% Notes on RxInfer

We searched GitHub for open issues in Julia libraries involving difficult-to-find NaNs.
In our first batch of issues, we found the ``RxInfer.jl'' library with an issue\footnote{\url{https://github.com/biaslab/RxInfer.jl/issues/116}} revolving around NaN detection.
We offered our tool for the package authors to use, and within a day the authors were able to track down the location of a NaN and fix the issue---all with minimal guidance.

@@

We would also like to thank the developers of RxInfer.jl for providing us with feedback on how we could make our tools more useful.
